\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-14 paper/experiments.tex
paper: add new generated tables + experiments changes

\begin{table}
  \centerfloat
  \input{runtimes}
    \caption{Error ($\epsilon$, planning time ($t_p$), and running time ($t_r$)i or queries
    with different imputation levels. Base error is the RMSE between the query run on clean
    data and the query run on dirty data without imputation. \todo{Micah: Not clear to me
    what the symbol means.}}
  \label{fig:experiments}
\end{table}

@@

Planning times are not shown\todo{they are shown...}, as they are fractions of a second for all of the queries that we tested.
The overall low planning times highlight the practicality of our algorithm, despite the exponential complexity.
Running times clearly vary based on $\alpha$, allowing users to tune their query performance as desired.

@@

\todo{consider giving up on getting the references to work?}
\begin{itemize}
\item For sum and count queries (\ref{q1}, \ref{q2}, \ref{q4}), imputation does a good job of reducing the error.
For each of these queries, we can reduce total error by several orders of magnitude.
Imputation performs very well in these cases, even for data which is missing uniformly at random, because each missing value directly increases the error of the result.

>>>>

\begin{table}
  \centerfloat
  \input{runtimes}
    \caption{Error ($\epsilon$, planning time ($t_p$), and running time ($t_r$)i or queries
    with different imputation levels. Base error is the root-mean-square error (RMSE) between the query run on clean
    data and the query run on dirty data without imputation.}
  \label{fig:experiments}
\end{table}

@@

Planning times are not shown, as they are fractions of a second for all of the queries that we tested.
The overall low planning times highlight the practicality of our algorithm, despite the exponential complexity.
Running times clearly vary based on $\alpha$, allowing users to tune their query performance as desired.

@@

\begin{itemize}
\item For sum and count queries (\ref{q1}, \ref{q2}, \ref{q4}), imputation does a good job of reducing the error.
For each of these queries, we can reduce total error by several orders of magnitude.
Imputation performs very well in these cases, even for data which is missing uniformly at random, because each missing value directly increases the error of the result.

### 2016-12-14 paper/queries.tex
paper: add new generated tables + experiments changes

\begin{tabular}{ll}
\toprule
\# & Query \\
\midrule
0 & \verb|SELECT BLD FROM acs;| \label{q0} \\
1 & \verb|SELECT BLD as units_in_structure, COUNT(ST) as estimate FROM acs GROUP BY BLD;| \label{q1} \\
2 & \verb|SELECT BATH as has_bath, COUNT(ST) as ct FROM acs GROUP BY BATH;| \label{q2} \\
3 & \verb|SELECT ACR as lotsize, AVG(BDSP) as avg_num_bedrooms FROM acs GROUP BY ACR;| \label{q3} \\
4 & \verb|SELECT PSF as has_sub_families, SUM(NP) as num_people FROM acs GROUP BY PSF;| \label{q4} \\
5 & \verb|SELECT AVG(NP) as avg_num_people FROM acs;| \label{q5} \\
6 & \verb|SELECT BDSP as num_bedrooms, AVG(ACR) as avg_lot_size FROM acs WHERE VEH >= 2 GROUP BY BDSP;| \label{q6} \\
\bottomrule
\end{tabular}

>>>>

\newcounter{queryno}
\begin{tabular}{cl}
\toprule
\# & \multicolumn{1}{c}{Query} \\
\midrule
1 & \verb|SELECT BLD as units_in_structure, COUNT(ST) as estimate FROM acs GROUP BY BLD;| \refstepcounter{queryno} \label{q1} \\
2 & \verb|SELECT BATH as has_bath, COUNT(ST) as ct FROM acs GROUP BY BATH;| \refstepcounter{queryno} \label{q2} \\
3 & \verb|SELECT ACR as lotsize, AVG(BDSP) as avg_num_bedrooms FROM acs GROUP BY ACR;| \refstepcounter{queryno} \label{q3} \\
4 & \verb|SELECT PSF as has_sub_families, SUM(NP) as num_people FROM acs GROUP BY PSF;| \refstepcounter{queryno} \label{q4} \\
5 & \verb|SELECT AVG(NP) as avg_num_people FROM acs;| \refstepcounter{queryno} \label{q5} \\
6 & \verb|SELECT BDSP as num_bedrooms, AVG(ACR) as avg_lot_size FROM acs WHERE VEH >= 2 GROUP BY BDSP;| \refstepcounter{queryno} \label{q6} \\
7 & \verb|SELECT MIN(YBL) as earliest_built_bucket FROM acs WHERE ACR = 3;| \refstepcounter{queryno} \label{q7} \\
8 & \verb|SELECT MIN(RMSP) as min_num_rooms FROM acs WHERE RWAT=2;| \refstepcounter{queryno} \label{q8} \\
9 & \verb|SELECT * FROM acs WHERE REFR = 1 AND STOV = 1 AND TEL = 1 AND TOIL = 2;| \refstepcounter{queryno} \label{q9} \\
10 & \verb|SELECT * FROM dirty m where m.f1 >= 2;| \refstepcounter{queryno} \label{q10} \\
11 & \verb|SELECT * FROM dirty where dirty.f1 <= 2;| \refstepcounter{queryno} \label{q11} \\
12 & \verb|SELECT MAX(f2) as max_f2 FROM dirty GROUP BY dirty.f1;| \refstepcounter{queryno} \label{q12} \\
13 & \verb|SELECT m1.f1, m1.f2 FROM dirty m1, clean m2 WHERE m1.f1 = m2.f1 and m1.f1 = 1 and m2.f2 = 69;| \refstepcounter{queryno} \label{q13} \\
14 & \verb|SELECT d1.f1 FROM dirty d1, clean d2 WHERE d1.f1 = d2.f1 and d2.f2 = 50;| \refstepcounter{queryno} \label{q14} \\
\bottomrule
\end{tabular}
